### 2022-03-09 src/text/1-introduction.tex
Fix pre commit hooks

\begin{figure}[t]
	\centering
	\includegraphics[height=0.5\textwidth,
		angle=270]{static/gammapy-big-picture} \caption{ Gammapy is a Python package
		for high-level gamma-ray data analysis. Using event lists, exposures and point
		spread functions as input you can use it to generate science results such as
		images, spectra, light curves or source catalogs. So far it has been used to
		simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT data, hopefully it
		will also be applied to e.g. VERITAS, MAGIC or HAWC data in the future. }
	\label{fig:big-picture}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[height=0.5\textwidth,
		angle=270]{static/gammapy-big-picture} \caption{ Gammapy is a Python package
		for high-level gamma-ray data analysis. Using event lists, exposures and point
		spread functions as input you can use it to generate science results such as
		images, spectra, light curves or source catalogs. So far it has been used to
		simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT data, hopefully it
		will also be applied to e.g., VERITAS, MAGIC or HAWC data in the future. }
	\label{fig:big-picture}

### 2022-03-09 src/text/2-package-subsections/catalog.tex
fix test fails
Fix pre commit hooks

Comprehensive source catalogs are increasingly being provided by many high energy astrophysics experiments. gammapy.catalog provides a convenient access to some common gamma-ray catalogs. A global catalog table is provided, along with source models flux points and light curves (if available) for individual objects, which are internally created from the supplied FITS tables. This module works independently from the rest of teh package, and the required catalogs are supplied in GAMMAPY_DATA. Presently, catalogs from Fermi-LAT (standard \citep{3FGL, 4FGL} and high energy \citep{2FHL, 3FHL}), H.E.S.S. galactic plane survey \citep{HGPS}, HAWC \citep{2HWC, 3HWC} and gamma-cat (\citep{gamma-cat}; an open source gamma ray catalog combining information from multiple catalogs) are supported.

>>>>

Comprehensive source catalogs are increasingly being provided by many high
energy astrophysics experiments. gammapy.catalog provides a convenient access
to some common gamma-ray catalogs. A global catalog table is provided, along
with source models flux points and light curves (if available) for individual
objects, which are internally created from the supplied FITS tables. This
module works independently from the rest of the package, and the required
catalogs are supplied in GAMMAPY\_DATA. Presently, catalogs from Fermi-LAT
(standard~\citep{3FGL, 4FGL} and high energy~\citep{2FHL, 3FHL}), H.E.S.S.
galactic plane survey~\citep{HGPS}, HAWC~\citep{2HWC, 3HWC} and gamma-cat
~\citep{gamma-cat}; an open source gamma ray catalog combining information from
multiple catalogs) are supported.

### 2022-03-09 src/text/2-package-subsections/datasets.tex
Fix pre commit hooks

The end product of the data reduction process described in Section
\ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps,
at the DL4 level. The gammapy.datasets subpackage contains classes to bundle
together binned data along with associated models and the likelihood, which
provides an interface to the Fit class (Sec \ref{ssec:gammapy-modeling}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistics, different types of Datasets are supported. MapDataset is
used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
done using SpectrumDatastet. While the default statistics for both of these is
Cash, their corresponding OnOff versions are adapted for the case where the
background is measured from real off counts, and support wstat statistics. The
predicted counts are computed by convolution of the models with the associate
IRFs. Fitting of precomputed flux points is enabled through FluxPointsDatasets,
using chi2 statistics. Multiple datasets of same or different types can be
bundled together in Datasets (e.g.: Figure \ref{fig*:minted:gp_datasets}),
where the likelihood from each constituent member is added, thus facilitating
joint fitting across different observations, and even different instruments
across different wavelengths. Datasets also provide functionalities for
manipulating reduced data, eg: stacking, sub-grouping, plotting, etc. Users can
also create their customized datasets for implementing modified likelihood
methods.

>>>>

The end product of the data reduction process described in Section
\ref{ssec:gammapy-makers} are a set of binned counts, background and IRF maps,
at the DL4 level. The gammapy.datasets subpackage contains classes to bundle
together binned data along with associated models and the likelihood, which
provides an interface to the Fit class (Sec \ref{ssec:gammapy-modeling}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistics, different types of Datasets are supported. MapDataset is
used for 3D (spectral and morphological) fitting, and a 1D spectral fitting is
done using SpectrumDatastet. While the default statistics for both of these is
Cash, their corresponding OnOff versions are adapted for the case where the
background is measured from real off counts, and support wstat statistics. The
predicted counts are computed by convolution of the models with the associate
IRFs. Fitting of precomputed flux points is enabled through FluxPointsDatasets,
using chi2 statistics. Multiple datasets of same or different types can be
bundled together in Datasets (e.g., Figure \ref{fig*:minted:gp_datasets}),
where the likelihood from each constituent member is added, thus facilitating
joint fitting across different observations, and even different instruments
across different wavelengths. Datasets also provide functionalities for
manipulating reduced data, eg: stacking, sub-grouping, plotting, etc. Users can
also create their customized datasets for implementing modified likelihood
methods.

### 2022-03-09 src/text/2-package-subsections/modeling.tex
Fix footnote
Fix pre commit hooks

The Fit class provides methods to fit, i.e. optimise parameters and estimate
parameter errors and correlations. It interfaces with a Datasets object, which
in turn is connected to a Models object containing the model parameters in its
Parameters object.  Models can be unique for a given dataset, or contribute to
multiple datasets and thus provide links, allowing e.g. to do a joint fit to
multiple IACT datasets, or to a joint IACT and \textit{Fermi}-LAT dataset. Many
examples are given in the tutorials.

The Fit class provides a uniform interface to multiple fitting backends:
“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
and errors are computed only for the fitting with MINUIT. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported Fit backend, including for example MCMC solutions.
\footnote{a prototype is available in gammapy-recipes,

	\url(https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html)}

>>>>

The Fit class provides methods to fit i.e., optimise parameters and estimate
parameter errors and correlations. It interfaces with a Datasets object, which
in turn is connected to a Models object containing the model parameters in its
Parameters object.  Models can be unique for a given dataset, or contribute to
multiple datasets and thus provide links, allowing e.g., to do a joint fit to
multiple IACT datasets, or to a joint IACT and \textit{Fermi}-LAT dataset. Many
examples are given in the tutorials.

The Fit class provides a uniform interface to multiple fitting backends:
“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
and errors are computed only for the fitting with MINUIT. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported Fit backend, including for example MCMC solutions.
\footnote{a prototype is available in gammapy-recipes,
	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
}

### 2022-03-09 src/text/3-applications.tex
Fix pre commit hooks

Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
In this section, we show a non-exhaustive list of some typical analysis that can be performed.
In general from the \gammapy side there is not limitation on which kind of analysis can be
done with wich instrument, however in practice it is limited by the availability of public data.

>>>>

Gammapy can be used for a variety of science cases by different IACT
experiments. (Refer to publications) In this section, we show a non-exhaustive
list of some typical analysis that can be performed. In general from the
\gammapy side there is not limitation on which kind of analysis can be done
with which instrument, however in practice it is limited by the availability of
public data.
